A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and coral bleaching as an alternate stable state

### 2017-03-22 JTB_ms/JTB_ms.tex
make with changes

  \begin{abstract}
  Coral reef ecosystems owe their ecological success--and vulnerability to
  climate change--to the symbiotic metabolism of corals and
  \emph{Symbiodinium} spp. The urgency to understand and predict the
  stability and breakdown of these symbioses (i.e., coral `bleaching')
  demands the development and application of theoretical tools. Here, we
  develop a dynamic bioenergetic model of coral-\emph{Symbiodinium}
  symbioses that demonstrates realistic steady-state patterns in coral
  growth and symbiont abundance across gradients of light, nutrients, and
  feeding. Furthermore, by including a mechanistic treatment of
  photo-oxidative stress, the model displays dynamics of bleaching and
  recovery that can be explained as transitions between alternate stable
  states. These dynamics reveal that `healthy' and `bleached' states
  correspond broadly to nitrogen- and carbon-limitation of the system,
  with transitions between them occurring as integrated responses to
  multiple environmental factors. Indeed, a suite of complex emergent
  behaviors reproduced by the model (e.g., bleaching is exacerbated by
  nutrients and attenuated by feeding) suggests it unifyingly captures
  many important attributes of the system; meanwhile, its modular
  framework and open source R code are designed to facilitate further
  problem-specific development. We see significant potential for this
  modeling framework to generate testable hypotheses and predict
  integrated, mechanistic responses of corals to environmental change,
  with important implications for understanding the performance and
  maintenance of symbiotic systems.
  \end{abstract}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Develop a new module of photo-oxidative stress.} Of primary
  interest to coral biologists and ecologists is symbiosis dysfunction
  under environmental stress, resulting in coral ``bleaching''--the loss
  of algal symbionts from the association (Jokiel and Coles 1977).
  Bleaching is thought to be triggered by photo-oxidative stress in
  \emph{Symbiodinium} (Weis 2008), which has been modeled previously as
  a response to absolute external irradiance (Eynaud, Nisbet, and Muller
  2011). However, this response may also depend on self-shading by other
  symbionts (Enríquez, Méndez, and Iglesias-Prieto 2005),
  CO\textsubscript{2} availability at the site of photosynthesis
  (Wooldridge 2009), and other non-photochemical quenching mechanisms
  (Roth 2014). We incorporate these features into a new photo-oxidative
  stress module linking overreduction of the photosynthetic light
  reactions to downstream impacts of photoinhibition and photodamage.
  Importantly, this formulation introduces a link between
  CO\textsubscript{2}-limitation of photosynthesis and bleaching, and
  potential synergistic roles for heterotrophy and nutrient availability
  in influencing bleaching responses (Wooldridge 2014b)
\item
  \emph{Reduce theoretical and mathematical complexity.} Following the
  logic of Jager, Martin, and Zimmer (2013), we exclude certain features
  of formal DEB theory in order to capture behaviors of interest with
  the simplest possible formulation. Here, we present a model without
  reserves, maturity, or reproduction (see Kooijman 2010). This
  formulation precludes modeling the full life cycle of corals as
  reproduction, larval stages, and metamorphosis are not considered, but
  greatly reduces theoretical complexity and parameter numbers, which is
  advantageous given the relative paucity of data for corals. Moreover,
  dynamics of the symbiosis (i.e., changes in symbiont to host biomass,
  including bleaching and recovery) and coral biomass growth are
  efficiently captured with this simpler formulation, which also
  increases accessibility for biologists and ecologists without
  requiring significant expertise in DEB theory.
\item
  \emph{Provide well-documented, open-access code.} In order to
  facilitate the continued development and application of theoretical
  modeling tools for coral symbioses, we provide open access to the
  model in the form of detailed, commented code written in the R
  language (R Core Team 2014). With an accessible and modular framework,
  we envision this model as a resource for further development by the
  scientific community to include additional complexity and
  problem-specific components. We chose the R language, which is freely
  available and in common use by biologists and ecologists, to reach the
  widest possible audience with this work.
\end{enumerate}

@@

Environmental stress is implemented in the form of photooxidative
stress, which is thought to be a primary trigger of coral bleaching
(Lesser 1997; Weis 2008; Wooldridge 2009). To simulate bleaching, we
model the absorption and quenching of light energy by photochemistry and
non-photochemical quenching, and the responses that occur (i.e.,
photoinhibition, photodamage, and symbiont loss) when these quenching
capacities are overwhelmed. While bleaching in response to high light
alone has been observed experimentally (Schutter et al. 2011; Downs et
al. 2013), mass coral bleaching events occur concurrently with high
temperature (Hoegh-Guldberg 1999). Thus, it is important to justify our
consideration of light as the primary stressor. In reality, light and
temperature interact synergistically (Coles and Jokiel 1978; Jones et
al. 1998), and in fact, any stressor that disrupts the quenching of
light energy may lead to bleaching (Wooldridge 2010; Baker and Cunning
2015). This is because the proximate cause of photo-oxidative stress is
excess excitation energy, but the upstream events that lead to this
situation may be diverse: indeed, elevated temperature may inhibit
Rubisco functioning (Jones et al. 1998) and the repair of the D1 protein
in photosystem II (Warner, Fitt, and Schmidt 1999), which reduces the
capacity of photochemical quenching and leads to an excess of light
energy. In this way, elevated temperature serves to reduce the threshold
above which light stresses the system (Hoegh-Guldberg 1999);
importantly, light is still the proximate stressor. Therefore, we
omitted temperature from the model to maintain a desired level of
simplicity, while still allowing photooxidative stress and bleaching to
be simulated with biological realism in response to light.

@@

\begin{longtable}[]{@{}llll@{}}

@@

\begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Symbol\strut
\end{minipage} & \begin{minipage}[b]{0.44\columnwidth}\raggedright\strut
Description\strut
\end{minipage} & \begin{minipage}[b]{0.26\columnwidth}\raggedright\strut
Units\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Eq. no.\strut
\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_X\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Prey uptake rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol X C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
3\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_N\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Nitrogen uptake rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N Cmol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
4\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{HG}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Host biomass formation rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
5\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{HT}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Host biomass turnover rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
6\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{NH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled nitrogen from host turnover\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
7\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(\rho_N\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Nitrogen shared with the symbiont\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
8\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{eC}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Excess carbon used to activate host CCMs\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol C C-mol H\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
9\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{CO_2}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
CO\textsubscript{2} input to photosynthesis\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
10\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_L\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Light absorption rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
12\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{CH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from host turnover\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
13\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{CS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from symbiont turnover\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
14\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{CP}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Photosynthesis rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
15\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{eL}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Light energy in excess of photochemistry\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
16\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{NPQ}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Total capacity of NPQ\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
17\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(c_{ROS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
ROS production proportional to baseline\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
18\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(r_{NS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Recycled nitrogen from symbiont turnover\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol N C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
19\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{SG}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Symbiont biomass formation rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
20\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(\rho_C\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Fixed carbon shared with host\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
21\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(j_{ST}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
Symbiont biomass turnover rate\strut
\end{minipage} & \begin{minipage}[t]{0.26\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
22\strut
\end{minipage}\tabularnewline

@@

\begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
Symbol\strut
\end{minipage} & \begin{minipage}[b]{0.44\columnwidth}\raggedright\strut
Description\strut
\end{minipage} & \begin{minipage}[b]{0.24\columnwidth}\raggedright\strut
Units\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Value\strut
\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(n_{NH}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
N:C molar ratio in host biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.18\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(n_{NS}\)\strut
\end{minipage} & \begin{minipage}[t]{0.44\columnwidth}\raggedright\strut
N:C molar ratio in symbiont biomass\strut
\end{minipage} & \begin{minipage}[t]{0.24\columnwidth}\raggedright\strut
--\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.13\)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
\(n_{NX}\)\strut

>>>>

  \begin{abstract}
  Coral reef ecosystems owe their ecological success--and vulnerability to
  climate change--to the symbiotic metabolism of corals and
  \emph{Symbiodinium} spp. The urgency to understand and predict the
  stability and breakdown of these symbioses (i.e., coral `bleaching')
  demands the development and application of theoretical tools. Here, we
  develop a dynamic bioenergetic model of coral-\emph{Symbiodinium}
  symbioses that demonstrates realistic steady-state patterns in coral
  growth and symbiont abundance across gradients of light, nutrients, and
  feeding. Furthermore, by including a mechanistic treatment of
  photo-oxidative stress, the model displays dynamics of bleaching and
  recovery that can be explained as transitions between alternate stable
  states. These dynamics reveal that `healthy' and `bleached' states
  correspond broadly to nitrogen- and carbon-limitation in the system,
  with transitions between them occurring as integrated responses to
  multiple environmental factors. Indeed, a suite of complex emergent
  behaviors reproduced by the model (e.g., bleaching is exacerbated by
  nutrients and attenuated by feeding) suggests it captures many important
  attributes of the system; meanwhile, its modular framework and open
  source R code are designed to facilitate further problem-specific
  development. We see significant potential for this modeling framework to
  generate testable hypotheses and predict integrated, mechanistic
  responses of corals to environmental change, with important implications
  for understanding the performance and maintenance of symbiotic systems.
  \end{abstract}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \emph{Develop a new module of photo-oxidative stress.} Of primary
  interest to coral biologists and ecologists is symbiosis dysfunction
  under environmental stress, resulting in coral ``bleaching''--the loss
  of algal symbionts from the association (Jokiel and Coles 1977).
  Bleaching is thought to be triggered by photo-oxidative stress in
  \emph{Symbiodinium} (Weis 2008), which has been modeled previously as
  a response to absolute external irradiance (Eynaud, Nisbet, and Muller
  2011). However, this response may also depend on self-shading by other
  symbionts (Enríquez, Méndez, and Iglesias-Prieto 2005),
  CO\textsubscript{2} availability at the site of photosynthesis
  (Wooldridge 2009), and other non-photochemical quenching mechanisms
  (Roth 2014). We incorporate these features into a new photo-oxidative
  stress module linking overreduction of the photosynthetic light
  reactions to downstream impacts of photoinhibition and photodamage.
  Importantly, this formulation introduces a link between
  CO\textsubscript{2}-limitation of photosynthesis and bleaching, and
  potential synergistic roles for heterotrophy and nutrient availability
  in influencing bleaching responses (Wooldridge 2014b)
\item
  \emph{Reduce theoretical and mathematical complexity.} Following the
  logic of Jager, Martin, and Zimmer (2013), we exclude certain features
  of formal DEB theory in order to capture behaviors of interest with
  the simplest possible formulation. Here, we present a model without
  reserves, maturity, or reproduction (see Kooijman 2010). This
  formulation precludes modeling the full life cycle of corals as
  reproduction, larval stages, and metamorphosis are not considered, but
  greatly reduces theoretical complexity and parameter numbers, which is
  advantageous given the relative paucity of data for corals. Moreover,
  dynamics of the symbiosis (i.e., changes in symbiont to host biomass,
  including bleaching and recovery) and coral biomass growth are
  efficiently captured with this simpler formulation, which also
  increases accessibility for biologists and ecologists without
  requiring expertise in DEB theory.
\item
  \emph{Provide well-documented, open source code.} In order to
  facilitate the continued development and application of theoretical
  modeling tools for coral symbioses, we provide open access to the
  model in the form of detailed, commented code written in the R
  language (R Core Team 2014). With an accessible and modular framework,
  we envision this model as a resource for further development by the
  scientific community to include additional complexity and
  problem-specific components. We chose R, an open source programming
  language in common use by biologists and ecologists, to reach the
  widest possible audience with this work.
\end{enumerate}

@@

Environmental stress is implemented in the form of photooxidative
stress, which is thought to be a primary trigger of coral bleaching
(Lesser 1997; Weis 2008; Wooldridge 2009). To simulate bleaching, we
model the absorption and quenching of light energy by photochemistry and
non-photochemical quenching, and the responses that occur (i.e.,
photoinhibition, photodamage, and symbiont loss) when these quenching
capacities are overwhelmed. While bleaching in response to high light
alone has been observed experimentally (Schutter et al. 2011; Downs et
al. 2013), mass coral bleaching events occur concurrently with high
temperature (Hoegh-Guldberg 1999). Thus, it is important to justify our
consideration of light as the primary stressor. In reality, light and
temperature interact synergistically (Coles and Jokiel 1978; Jones et
al. 1998), and in fact, any stressor that disrupts the quenching of
light energy may lead to bleaching (Wooldridge 2010; Baker and Cunning
2015). This is because the proximate cause of photo-oxidative stress is
excess excitation energy, but the upstream events that lead to this
situation may be diverse. Indeed, elevated temperature may inhibit
Rubisco functioning (Jones et al. 1998) and the repair of the D1 protein
in photosystem II (Warner, Fitt, and Schmidt 1999), which reduces the
capacity of photochemical quenching and leads to an excess of light
energy. In this way, elevated temperature serves to reduce the threshold
above which light stresses the system (Hoegh-Guldberg 1999);
importantly, light is still the proximate stressor. Therefore, we
omitted temperature from the model to maintain a desired level of
simplicity, while still allowing photooxidative stress and bleaching to
be simulated with biological realism in response to light.

@@

\begin{longtable}[c]{@{}llll@{}}

@@

\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Symbol
\strut\end{minipage} &
\begin{minipage}[b]{0.45\columnwidth}\raggedright\strut
Description
\strut\end{minipage} &
\begin{minipage}[b]{0.27\columnwidth}\raggedright\strut
Units
\strut\end{minipage} &
\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Eq. no.
\strut\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_X\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Prey uptake rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol X C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
3
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_N\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Nitrogen uptake rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N Cmol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
4
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HG}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Host biomass formation rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
5
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{HT}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Host biomass turnover rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol H C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
6
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled nitrogen from host turnover
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
7
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\rho_N\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Nitrogen shared with the symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
8
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{eC}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Excess carbon used to activate host CCMs
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol C C-mol H\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
9
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CO_2}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
CO\textsubscript{2} input to photosynthesis
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
10
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_L\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Light absorption rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
12
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{CH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from host
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
13
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{CS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled CO\textsubscript{2} from symbiont
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut

@@

d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
14
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{CP}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Photosynthesis rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
15
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{eL}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Light energy in excess of photochemistry
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
16
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{NPQ}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Total capacity of NPQ
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol photons C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
17
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(c_{ROS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
ROS production proportional to baseline
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
18
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(r_{NS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Recycled nitrogen from symbiont turnover
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol N C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
19
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{SG}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Symbiont biomass formation rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
20
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(\rho_C\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Fixed carbon shared with host
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
mol C C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
21
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(j_{ST}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
Symbiont biomass turnover rate
\strut\end{minipage} &
\begin{minipage}[t]{0.27\columnwidth}\raggedright\strut
C-mol S C-mol S\textsuperscript{-1} d\textsuperscript{-1}
\strut\end{minipage} &
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
22
\strut\end{minipage}\tabularnewline

@@

\begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
Symbol
\strut\end{minipage} &
\begin{minipage}[b]{0.45\columnwidth}\raggedright\strut
Description
\strut\end{minipage} &
\begin{minipage}[b]{0.25\columnwidth}\raggedright\strut
Units
\strut\end{minipage} &
\begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Value
\strut\end{minipage}\tabularnewline

@@

\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NH}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
N:C molar ratio in host biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.18\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NS}\)
\strut\end{minipage} &
\begin{minipage}[t]{0.45\columnwidth}\raggedright\strut
N:C molar ratio in symbiont biomass
\strut\end{minipage} &
\begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
--
\strut\end{minipage} &
\begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
\(0.13\)
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
\(n_{NX}\)
